\documentclass[letterpaper,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{cite}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}

\begin{document}

\title{WMConv: Worklist-driven Masked Convolution\\
for Onboard High-Speed Robotic Perception}

\author{Anonymous Authors% <-this % stops a space
\thanks{Manuscript received Month DD, YYYY.}}

% The paper headers
\markboth{IEEE Robotics and Automation Letters. Preprint Version.}%
{Author \MakeLowercase{\textit{et al.}}: WMConv: Worklist-driven Masked Convolution}

\maketitle

\begin{abstract}
Onboard robotic perception must run convolutional networks within tight
latency and power budgets, so many high-speed vision systems produce a
spatial active mask and update only the convolution outputs tied to the
active regions. Yet existing execution paths for such masked convolution
sit at opposite ends of a trade-off between useful-compute ratio and
throughput: tile skipping keeps the dense pipeline's throughput but skips
too coarsely, while gather-scatter skips precisely but collapses
throughput, so high sparsity rarely becomes a comparable latency speedup.
We present WMConv, a worklist-driven dense-grid masked convolution operator
that fuses the gather into the convolution kernel and sparsifies only the
output positions to compute, retaining the dense pipeline while skipping at
position granularity. A lightweight, tiled worklist-construction stage
resolves both the coordinate-discovery and locality-preservation overheads
at once. On the Jetson Xavier NX and Orin, across three mask sources and
three robotic perception tasks, WMConv converts sparsity into on-device
latency reduction and higher perception frequency more effectively than
dense cuDNN, tile skipping, and gather-scatter baselines, while preserving
task accuracy.
\end{abstract}

\begin{IEEEkeywords}
Computer architecture for robotic and automation, software, deep learning
methods, sparse convolution, embedded perception.
\end{IEEEkeywords}

\input{src/intro}
\input{src/background}

% ---------------------------------------------------------------------------
% Remaining sections (to be written):
% \input{src/related}
% \input{src/method}
% \input{src/eval}
% \input{src/conclusion}
% ---------------------------------------------------------------------------

\section*{Acknowledgments}
% TODO

\bibliographystyle{IEEEtran}
\bibliography{refs}

\end{document}
