\section{Evaluation}
\label{sec:eval}

\subsection{Experimental Setup}
\label{sec:eval:setup}

We evaluate \sysname on four GPU platforms, three robotic perception tasks
with distinct mask sources, and three baselines representing the dense,
tile-skipping, and gather-scatter paradigms.

\subsubsection{Platforms}
Experiments run on two embedded platforms representative of onboard robotic
deployment and two desktop-class GPUs that test generality:
Jetson Xavier NX (8\,GB, CUDA~11.4),
Jetson AGX Orin (64\,GB, CUDA~11.4),
RTX~4070 Laptop (CUDA~12.1), and
RTX~3080 Desktop (CUDA~12.1).
% TODO: Jetson power mode, clock settings if fixed.

\subsubsection{Models, Tasks, and Mask Sources}

Table~\ref{tab:models} summarizes the three evaluation workloads. Each
pairs a robotic perception task with a mask source drawn from a different
family (Section~\ref{sec:bg:masks}).

\begin{table}[t]
\centering
\caption{Evaluation workloads.}
\label{tab:models}
\begin{tabular}{lccc}
\hline
 & \textbf{FireFlowNet} & \textbf{YOLO} & \textbf{ResNet} \\
\hline
Task & Optical flow & Object detection & Depth estimation \\
Mask source & EvConv & DeltaCNN & DGNet \\
Dataset & MVSEC & MOT16 & KITTI \\
Resolution & $346{\times}260$ & $640{\times}640$ & $1280{\times}384$ \\
\#Parameters & TODO & TODO & TODO \\
Dataset size & TODO & TODO & TODO \\
\hline
\end{tabular}
\end{table}

\textbf{Optical flow.} We use FireFlowNet~\cite{fireflownet}, a lightweight
eight-convolution optical-flow network, with EvConv~\cite{evconv} as the mask
source. Following the EvConv protocol, each input encodes a 50-ms event window
and consecutive inferences shift this window by 1 ms. We calibrate threshold
and kernel-selection policies on \texttt{indoor\_flying1}, exclude that
sequence from evaluation, and report results on \texttt{indoor\_flying2},
\texttt{indoor\_flying3}, and \texttt{outdoor\_day1}~\cite{mvsec}. We select
one global sparsification threshold from three calibration regions that span
low and high event activity. We then derive input-activity buckets and their
per-layer kernel configurations from a streaming replay of the complete
calibration sequence. The threshold is chosen at the knee of the aggregate
AEE and scheduled-FLOP tradeoff; per-region accuracy remains a diagnostic
rather than a runtime guarantee. We report per-sequence AEE on all held-out
sequences.

\textbf{Object detection.} We use YOLOv11~\cite{yolov11}
with temporal frame differences as the mask source
(DeltaCNN~\cite{deltacnn}): consecutive frames are differenced and
positions exceeding a threshold % TODO: threshold value
are marked active. We evaluate on the MOT16 dataset~\cite{mot16} with
$640{\times}640$ input resolution.

\textbf{Depth estimation.} We use a ResNet-34 encoder-decoder~\cite{monodepth2}
with DGNet~\cite{dgnet} learned spatial gating as the mask source: a
lightweight gating module predicts task-relevant regions per frame.
We evaluate on KITTI~\cite{kitti} ($1280{\times}384$ resolution).

FireFlowNet~\cite{fireflownet} and YOLOv11 % TODO: cite yolov11
use their respective official pretrained weights;
EvConv~\cite{evconv} and DeltaCNN~\cite{deltacnn} provide inference-time masks without modifying the pretrained model weights. For DGNet~\cite{dgnet}, the
gating module is jointly trained with the backbone following the default
DGNet configuration.

\subsubsection{Baselines}

We compare against three baselines, all running in FP32 on identical
hardware and inputs:
\begin{itemize}
  \item \textbf{Dense}: cuDNN~\cite{cudnn} implicit GEMM with best-algorithm selection
        via \texttt{cudnnFind}.
%   \item \textbf{Tile skipping}: DeltaCNN~\cite{deltacnn} execution engine.
%         DeltaCNN includes a delta-propagation optimization specific to
%         temporal frame differences or event-camera increments (computing and propagating only output
%         deltas). We enable delta propagation for the temporal frame difference and event-camera increment tasks
%         and disable it for the learned-gating task since it is not applicable.
%   \item \textbf{Tile skipping}: DeltaCNN~\cite{deltacnn} execution engine.
%         DeltaCNN performs a dense initialization, then differences consecutive
%         inputs, propagates sparse output deltas through cached intermediate
%         states, and skips tiles whose receptive fields contain no active
%         values. We use this incremental mode for both event-window increments
%         and temporal frame differences. Learned spatial gating instead selects
%         regions independently within each current-frame inference and does not
%         define temporal deltas for updating cached states; for this task, we
%         use only DeltaCNN's tile-skipping execution with the masks supplied by
%         the gating module.
  \item \textbf{Tile skipping}: DeltaCNN~\cite{deltacnn} execution engine.
        After a dense initialization, DeltaCNN differences consecutive inputs,
        propagates only sparse output deltas through cached intermediate states, and
        skips tiles with inactive receptive fields. We use this incremental
        mode optimization for event-window increments and temporal frame differences.
        Learned spatial gating provides per-inference region masks rather than
        temporal state updates, so we use only DeltaCNN's tile-skipping
        execution with the supplied gating masks.


  \item \textbf{Gather-scatter}: MMCV~\cite{mmcv} \texttt{MaskedConv2d}
        operator, which performs \texttt{masked\_im2col} (gather active
        patches), matrix multiply, and \texttt{masked\_col2im} (scatter
        back).
\end{itemize}

\subsubsection{Metrics and Methodology}

We report four metrics:
(1)~end-to-end latency (ms),
(2)~useful-compute ratio $\eta$ (Section~\ref{sec:bg:gap}),
(3)~throughput (GFLOPS, giga floating-point operations per second), and
(4)~task accuracy: Average Endpoint Error (AEE, pixels) for optical flow,
mean Average Precision (mAP, \%) for object detection, and Root Mean
Square Error (RMSE, meters) for depth estimation.
For optical-flow accuracy, the model processes every 1-ms window shift so that
incremental state evolves identically to the latency experiment. We sample a
prediction at the nearest MVSEC flow timestamp, with at most 0.5 ms alignment
error, and scale the predicted 50-ms flow by the ratio between the
ground-truth interval and 50 ms before computing AEE.
Latency measurements use per-frame CUDA events on the compute stream. Input
histogram construction and host-to-device transfer are excluded: pinned inputs
are copied on a dedicated stream with one-frame look-ahead, and the start event
is recorded after the compute stream has waited for that frame's copy. The
timed region includes input differencing, mask and worklist construction, all
network operators, runtime sparsity selection, and output accumulation. The
first-frame dense initialization and all calibration/autotuning are outside the
timed region. Events are synchronized and read in batches rather than after
each frame, preserving asynchronous runtime behavior. We run each complete
held-out sequence three times and report both mean and standard deviation and
median and median absolute deviation.

\subsection{End-to-End Latency}
\label{sec:eval:latency}

% TODO

\subsection{Efficiency Analysis}
\label{sec:eval:efficiency}

% TODO

\subsection{Construction Overhead}
\label{sec:eval:overhead}

% TODO

\subsection{Task Accuracy}
\label{sec:eval:accuracy}

% TODO
