\section{Implementation}
\label{sec:impl}

\sysname is implemented as a CUDA C++ library exposed to PyTorch via
Pybind11. The core masked convolution operator serves as a drop-in
replacement for \texttt{nn.Conv2d} with identical weights and
hyperparameters. To support end-to-end sparse execution of complete CNN
architectures, the library also provides mask-aware implementations of
\texttt{ConvTranspose2d}, pooling, element-wise addition, etc. All
operators accept and propagate the active mask; no model architecture
modification is required and existing pretrained weights load directly.
All tensors use the channels-last (NHWC) memory layout, so that reading
a spatially sparse set of positions still produces contiguous memory
accesses along the channel dimension, preserving throughput. 

The construction
kernel maps one thread per output position; each thread tests the receptive
field against $M_{in}$ with early exit. Within each warp,
\texttt{\_\_ballot\_sync} produces a bitmask of active lanes and
\texttt{\_\_popc} on masked prefixes yields each active lane's rank, giving
the support set $\mathcal{I}_n$ (the ordered indices of active positions)
without a sort or prefix-sum pass. One warp-elected thread performs a
single \texttt{atomicAdd} to reserve a contiguous worklist segment; each
active lane writes its index at the reserved base plus its rank.

The compute kernel follows a Cutlass-style~\cite{cutlass} implicit-GEMM
structure with double-buffered shared memory and asynchronous
global-to-shared loads (\texttt{cp.async} on Ampere+). Tile configurations
($B_M$, $B_N$, $B_K$) are selected via Triton-style~\cite{triton} offline
autotuning: for each unique
layer shape (spatial dimensions, channels, kernel size), a one-time
profiling sweep determines the best-performing tile, which is then reused
across all inference calls. The \sysname output is bit-identical to dense cuDNN convolution for all
active positions.
