% intro.tex --- Introduction section for the WISEConv RAL/ICRA letter.
% Meant to be \input{} from the main IEEEtran document.
% Bib keys used below (define in your .bib):
%   evconv, deltacnn, dgnet, torchsparsepp, spconv, cudnn
%
% Length target: ~3/4 to 1 column-page (RAL/ICRA letter). Keep it tight.

\section{Introduction}
\label{sec:intro}

\IEEEPARstart{O}{nboard} robots run convolutional perception in the control
loop for navigation, manipulation, and closed-loop
control~\cite{fastdepth,nanoflownet,contactgraspnet}. On embedded platforms
the available compute is far below server-class GPUs, yet perception latency
is a hard real-time constraint because it sits directly on the control path.
Dense convolution recomputes every spatial position, and on these platforms
it often cannot reach the update frequency the loop demands. Many
high-speed vision systems on UAVs, mobile robots, and embedded
devices~\cite{evconv,asyncsparse,deltacnn,dgnet} therefore concentrate
compute on active regions via \emph{masked convolution}: the input stays a
dense image-grid tensor, but only the outputs at positions marked active are
updated.

The standard dense convolution pipeline partitions the output grid into
\emph{tiles} (contiguous spatial blocks) and for each tile reads the
required input patch by coordinate, computes the convolution, and writes
the result back. This coordinate-driven, tile-based execution achieves high
throughput because tiles access spatially contiguous data with regular,
predictable memory patterns. Existing masked-convolution systems modify or
abandon this pipeline along two paths.

\emph{Tile skipping}~\cite{sbnet,skipconv,evconv,deltacnn} stays inside the
dense pipeline: it tests each tile and skips it if every position within is
inactive. Throughput is preserved for non-skipped tiles, but a single
active position forces the entire tile to execute, so many computed outputs
are unneeded. \emph{Gather-scatter}~\cite{dgnet,sai} abandons the pipeline
entirely: it extracts active positions exactly, gathers their input
neighborhoods, computes, and scatters results back. Every computed output is
needed, but the extraction, irregular memory access, and scatter writeback
collapse throughput.

We characterize this trade-off along two axes: \emph{throughput} (operations
per second, bounded by the dense pipeline) and \emph{useful-compute ratio}
(the fraction of executed operations that produce needed outputs). Tile
skipping preserves throughput but sacrifices useful-compute ratio;
gather-scatter achieves high useful-compute ratio but sacrifices throughput.
Neither delivers both, so upstream sparsity does not translate into
proportional latency reduction.
% TODO: fill measured numbers (XX/YY/AA/BB/CC/DD)
In our evaluation on Jetson Xavier NX and Orin, existing
methods~\cite{evconv,deltacnn,cbinfer,dgnet,sai} reduce the active-output ratio to
roughly \mbox{XX--YY\%}; yet tile-skipping methods achieve only
\mbox{AA--BB\%} useful-compute ratio, while gather-scatter methods reach
only \mbox{CC\%} of tile-skipping throughput. Convolution latency is reduced
by only \mbox{DD--EE\%}.

Our key insight is that the position-level selectivity of gather-scatter
can be fused into the dense pipeline's coordinate-driven execution without
the separate data-movement stages. The fusion is straightforward in
principle: because each tile already performs a coordinate-driven
read-compute-write per position, replacing the tile's coordinate source,
from a contiguous block to a set of active positions, gives position-level
selectivity while keeping the per-position execution path identical. This
achieves high useful-compute ratio directly, and because the per-position
datapath remains that of the dense pipeline, it opens the potential for
dense-level throughput.

Realizing this potential requires addressing the challenge of two practical overheads. First, \emph{coordinate discovery}: the kernel must
know which positions are active before computation begins, yet scanning for
them inside the compute kernel would stall the main datapath. Second,
\emph{locality}: if active positions are processed in arbitrary (instead of contiguous) order,
memory access loses the spatial regularity that gives the dense pipeline its
speed; a global sort would restore order but is itself expensive.

We present \sysname (\textbf{W}orkl\textbf{I}st-driven ma\textbf{S}k\textbf{E}d Convolution), a dense-grid masked
convolution operator that resolves both overheads through a two-stage
design. A lightweight construction stage scans the active mask and emits a
\emph{worklist}: the ordered coordinates of active output positions. The
subsequent compute stage drives the dense pipeline's coordinate-driven
execution with the worklist as its coordinate source, computing only the
active outputs. Both overheads are addressed by the
construction stage's tiled scan: it operates entirely in 2D mask space (no
feature data touched), so coordinate discovery costs only XX\% of the
compute-stage time; and it compacts active positions from each tile into
contiguous worklist segments, so the compute stage accesses spatially nearby
input data when processing consecutive worklist entries, preserving locality
comparable to the dense traversal without any global sort. With construction overhead minimized and only
active outputs computed, \sysname achieves near-linear latency scaling: an
active-output ratio of $x$\% yields convolution latency close to $x$\% of
the dense baseline.

This paper makes the following contributions:
\begin{itemize}
  \item We identify the useful-compute ratio vs.\ throughput trade-off as
        the fundamental bottleneck preventing masked convolution from
        delivering proportional speedup on embedded
        platforms~\cite{sbnet,skipconv,evconv,deltacnn,dgnet,sai}.
  \item We present \sysname, a worklist-driven masked convolution operator
        that fuses position-level selectivity into the dense pipeline's
        coordinate-driven execution, achieving both high useful-compute
        ratio and near-dense throughput.
  \item On Jetson Xavier NX and Orin, \sysname achieves near-linear latency
        scaling with active-output ratio across three mask sources and three
        robotic perception tasks, outperforming dense cuDNN, tile skipping,
        and gather-scatter while preserving task accuracy.
\end{itemize}
